---
title: "Introducing 'fulltext'"
author: "Andreas Blätte (andreas.blaette@uni-due.de)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fulltext}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

## Purpose


The ´fulltext´-package includes a lightweight htmlwidget for fulltext output.

## Getting Started

```{r, eval = TRUE}
library(janeaustenr)
library(tokenizers)
library(fulltext)
library(polmineR)
library(magrittr)
library(data.table)
```

## From tidytext to fulltext

```{r, eval = TRUE}
ftxt_list <- cut(1:length(emma), c(1, grep("^\\s*$", emma), length(emma))) %>%
  split(janeaustenr::emma, f = .) %>%
  lapply(paste, collapse = " ") %>%
  tokenizers::tokenize_words(lowercase = FALSE, strip_punct = FALSE) %>%
  as.fulltexttable() %>% 
  split(ftxt, column = "tag_before", regex = "<para") %>%
  retag(regex = "CHAPTER", old = "para", new = "h2") %>%
  as.fulltexttable() %>%
  split(column = "token", regex = "CHAPTER") %>%
  rename(name = sprintf("Chapter %d", seq_along(.)))
```


```{r, eval = TRUE}
fulltext(ftxt_list[[1]])
```


## From a subcorpus to fulltext

We introduce the fulltext package by example. In addition to the fulltext package, we need the polmineR package which includes the GERMAPARLMINI corpus.

```{r, eval = TRUE}
library(polmineR)
use("polmineR")
```

The example aims at outputting one particular speech. We take a speech held by Voker Kauder in the German Bundestag.

```{r, eval = TRUE}
sp <- corpus("GERMAPARLMINI") %>%
  subset(speaker == "Volker Kauder") %>%
  subset(date == "2009-11-10")
```

The data that is passed to the JavaScript that generates the output. Expected to be a list of lists that provide data on sections of text. Each of the sub-lists is to be a named list of a character vector with the HTML element the section will be wrapped into, and  a `data.frame` (or a list) with a column "token", and a column "id".

```{r, eval = TRUE}
ftab <- as.fulltexttable(sp, headline = "Volker Kauder (CDU)", display = "block")
```

So let us see the result ... 

```{r, eval = TRUE}
fulltext(ftab, box = TRUE)
```


## Crosstalking

### Preparations

```{r}
ftxt_list <- lapply(
  setNames(names(ftxt_list), names(ftxt_list)),
  function(chapter) data.frame(ftxt_list[[chapter]], chapter = chapter)
)
```



```{r}
library(crosstalk)
austen_chapters <- do.call(rbind, ftxt_list)
austen_chapters[["tag_before"]] <- gsub("display:block", "display:none", austen_chapters[["tag_before"]])
sd <- crosstalk::SharedData$new(austen_chapters, ~chapter, group = "fulltext")
chapters_table <- data.frame(chapter = unique(austen_chapters$chapter))
chapters_table_sd <- crosstalk::SharedData$new(chapters_table, ~chapter, group = "fulltext")

y <- bscols(
  # widths = c(NA,NA),
  DT::datatable(
    chapters_table_sd,
    options = list(lengthChange = TRUE, pageLength = 8L, pagingType = "simple", dom = "tp"),
    rownames = NULL, width = "100%", selection = "single"
  ),
  fulltext(sd, width = "100%", box = TRUE)
)

```

So this is the result.

```{r}
y
```

## Perspectives

Enjoy! 